Composition-climate paper

### 2015-05-12 Composition_Ecology.Rmd
Added the Natural Earth module, some text including explanation of climate trends.
Added overlapping distributions and text.

Setup R addes some code to allow NeturalEarth module to run.

Building small climate gives us the cropped PRISM data.

Modifications to Hellinger distance to allow direct comaprisons of intensity of shifts.

source('R/Setup_R.R')
source('R/load_climate.R') # gives then.clim & now.clim
source('R/load_veg.R')

@@

The shifts in distribution to lead to changes in the apparent climate envelopes of the taxa, but these are dwarfed by the shifts in regional climate across the area.
```{r densityplots, warning=FALSE, message=FALSE, echo=FALSE, fig.height = 10, fig.width=7}

source('R/resampling_climate.R')
source('R/figures//climate_boxplots.R')

@@

ggplot(all.hellinger, aes(x = fixedv_c, y = fixedc_v, color = climate)) +
  geom_point() + geom_abline(intercept=0, slope = 1) + facet_wrap(~shift) +
  xlab('Vegetation Fixed - Climate Shifting') +
  ylab('Climate Fixed - Vegetation Shifting') +
  theme_bw()

>>>>

source('R/Setup_R.R')
source('R/load_climate.R') # gives then.clim & now.clim
source('R/load_veg.R')
source('R/natural_earth.R')

@@

```{r changing_climate, warning=FALSE, message=FALSE, echo=FALSE}

source('R/figures/climate_ts.R')

changes <- modern$value - past$value
```

During this time climate has also changed.  Mean temperatures in the region show an average increase of `r round(changes[3], 2)`^o^C since the 1895-1925 normal.  Annual precipitation has increased slightly (`r round(changes[1], 0)`mm), and maximum annual temeprature has declined slightly (`r round(changes[2], 2`^o^C)).  The most significant change has been in annual minimum temperatures, which have increased by `r round(changes[4], 1)` since the 1895-1925 normal.  This broad scale increase in winter temperatures is widely accepted, and results in an overall shift in the winter 'climate space' for the region.

```{r densities}

source('R/resampling_climate.R')

source('overlapping_distributions.R')

```
**Figure** *Changes in the overall climate space in the upper midwestern United States. The climate densities largely overlap, although it is possible to see the shifts in precipitation, mean and minium temperatures, where FIA data (pink) has higher values), while the decline in maximum temperatures is also visible, largely at the very highest values.*

While these changes in climate are visible across the whole range, we would expect that species with significant shifts in distribution as a result of land use change in the post-settlement era should show changes that superceed the changes resulting from climate alone.  In particular, if the land use pressure is biased spatially or climatically then these changes should be even more dramatic.  Hellinger distance is used to understand the difference in the shape of kernel densities.  Using the distributions in climate space for each of the key taxa we can shift climate, or vegetation to understand the relative effects of land use change and climatic change across the region.

ggplot(all.hellinger, aes(x = fixedv_c, y = fixedc_v, color = climate)) +
  geom_point(size = 2) + 
  geom_abline(intercept=0, slope = 1) + 
  facet_grid(shift ~ climate) +
  xlab('Vegetation Fixed - Climate Shifting') +
  ylab('Climate Fixed - Vegetation Shifting') +
  theme_bw() +
  theme(axis.text = element_text(family = 'serif', size = 12),
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face='bold', size = 14),
        legend.title = element_text(family = 'serif', face='bold', size = 14))

The Hellinger distances reveal that

```{r densityplots, warning=FALSE, message=FALSE, echo=FALSE, fig.height = 10, fig.width=7}
source('R/figures//climate_boxplots.R')

@@
